### 2018-02-20 Chapters/Conclusion.tex
Minor changes

Finally, we have studied how variations of the Bass Model may reflect systems or technologies that may wither in time. Though some innovations, such as the radio, have gained widespread use in a sustainable form... One may want to review the Bass model when one is concerned with rapidly-evolving technological ecosystems.  Hardly anyone remembers the names AskJeeves, World Wide Web Worm, Lycos, WebCrawler, or AltaVista, early web search engines; later replaced, in the market and by the market, by the almost unnoticed url http://google.stanford.edu \citep{brin1998anatomy}.

>>>>

Finally, we have studied how variations of the Bass Model may reflect systems or technologies that may wither in time. Though some innovations, such as the radio, have gained widespread use in a sustainable form... One may want to review the Bass model when one is concerned with rapidly-evolving technological ecosystems.  Hardly anyone remembers the names AskJeeves, World Wide Web Worm, Lycos, WebCrawler, or AltaVista, early web search engines; later replaced, in the market and by the market, by the almost unnoticed url \url{http://google.stanford.edu} \citep{brin1998anatomy}.
